Cryptographic assurance of secrecy and fairness in voting

### 2012-12-07 paper/paper.tex
Improve caption on Helios mixnet depiction
more pret-a

\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations ?????}

@@

\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way. Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.

@@

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
	\caption{Re-encryption \term{mixnet}}
	\label{fig:mixnet}
\end{figure}

>>>>

@@

\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
\pv\ is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.

@@

\begin{figure}
	\center
	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
	\caption{Simple re-encryption \term{mixnet} like the one used in Helios}
	\label{fig:mixnet}
\end{figure}
